Corpus Analysis

### 2020-08-27 inst/analysis/corpus-stage2.Rmd
Fixes in pipeline

```{r}
package_runs <- trace_runs_raw %>%
  mutate(
    dir=as.character(path("../../run/package-evals-traced", package, basename(file))),
    file=as.character(path("./", basename(dirname(file)), basename(file))),
  ) %>%
  semi_join(corpus, by="package")

@@

package_programs <-
  left_join(
    package_programs, 
    transmute(package_programs_errors, error=paste(source, message, call), file), 
    by="file"
  ) %>%
  mutate(
    success=
      type %in% c("examples", "tests", "vignettes") & 
      !is.na(code) &
      !is.na(runtime) &
      code > 0 &
      is.na(error)
  )
```

@@

>>>>

```{r}
package_runs <- trace_runs_raw %>%
  mutate(
    dir=as.character(path("../../run/package-evals-traced.2", package, basename(file))),
    file=as.character(path("./", basename(dirname(file)), basename(file))),
  ) %>%
  semi_join(corpus, by="package") %>%
  mutate(
    call_file=path(paste0(tools::file_path_sans_ext(out_file), ".R"), "calls.fst")
  ) %>%
  filter(file.exists(call_file))

@@

package_programs <-
  left_join(
    package_programs, 
    transmute(package_programs_errors, error=paste(source, message, call), file), 
    by="file"
  ) %>%
  mutate(
    success=
      type %in% c("examples", "tests", "vignettes") & 
      !is.na(code) &
      !is.na(runtime) &
      code > 0 &
      is.na(error)
  )

package_programs <-
  package_programs %>%
  filter(file_exists(path(params$base_dir, str_replace(file, fixed("../../"), ""))))
```

@@

```{r remove tests, eval=FALSE}
df <- read_csv(path(params$base_dir, "runnable-code-metadata.csv"))
df <- mutate(df, file=path(params$base_dir, "run", "package-evals-traced.2", basename(package), basename(filename)), type=basename(dirname(filename)), file_e=dir.exists(file))
df <- filter(df, !(type %in% c("examples", "vignettes")), file_e)
```

```{r sanity check, eval=FALSE}
x <- read_fst("/var/lib/R/project-evalR/run/package-evals-traced.2/calls.fst")
y <- x %>% mutate(package=basename(dirname(dirname(file)))) %>% semi_join(corpus, by="package")
files <- count(as_tibble(y), file)
a <- anti_join(files, package_programs, by="file")
a
a$file %>% str_replace(fixed("../.."), params$base_dir) %>% dirname() %>% dir_exists()
```
